A GPU Implementation of Capon for an Active Sonar System

### 2012-05-04 ECUA2012/gpu_capon_ecua2012.tex
la2pdf commit - 2012:05:04	16:08:07	(Fri 4.May)

We have tested \gls{GPU} implementation of the \gls{MVDR} beamformer on experimental data from $M=32$ element Kongsberg Maritime HISAS1030 sonar~\cite{Hansen2009}\todo{specify SAS somewhere here..}. The sonar was attached to the HUGIN \gls{AUV}, and the imaged object was the 1500 dwt oil tanker wreck Holmengraa (fig. \ref{holmengraa}). Holmengraa is roughly 68\,m long and 9\,m wide, and lies on a slanted seabed at 77\,m depth.

>>>>

We have tested \gls{GPU} implementation of the \gls{MVDR} beamformer on experimental data from the $M=32$ element Kongsberg Maritime HISAS1030 sonar~\cite{Hansen2009}\todo{specify SAS somewhere here..}. The sonar was attached to the HUGIN \gls{AUV}, and the imaged object was the 1500 dwt oil tanker wreck Holmengraa (fig. \ref{holmengraa}). Holmengraa is roughly 68\,m long and 9\,m wide, and lies on a slanted seabed at 77\,m depth. The Capon image
